Magnitude of simple rules in investment strategies of algorithmic trading

### 2013-06-03 Article/Article20130603/tewi-paper-template.tex
Fig. size
poprawka podpisów osi w epsach na angielskim zmiana języka artykułu na angielski
literówka w adresie uczelni "Żolnierska" - > "Żołnierska"

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{amsthm}
\usepackage{txfonts}
\usepackage{epstopdf}
\usepackage{placeins}

\usepackage{polski}
\usepackage[utf8]{inputenc}
\usepackage[table]{xcolor}
\usepackage{array}
\usepackage{subcaption}

@@

\title{Magnitude of simple rules in investment strategies of algorithmic trading}
\headtitle{Magnitude of simple rules in investment strategies of algorithmic trading\dots}
\author{Antoni Wiliński\inst{1}, Piotr Błaszyński\inst{1}, Aneta Bera\inst{1}, \\ Wojciech Nowicki\inst{1}, Katarzyna Buda\inst{1}}
\headauthor{A. One, A. Two}
\affiliation{%
  \inst{1}West Pomeranian University of Technology\\
  Faculty of Computer Science\\
  ul.Żolnierska 49, 71-210 Szczecin Poland\\
  {awilinski,pblaszynski}@wi.ps.pl, @wi.ps.pl
}
\keywords{algorithmic trading, forecasting, financial markets, simple rules, computational intelligence, investment strategies}

@@

\begin{figure}[h]
\centering
\begin{minipage}{.49\linewidth}
\centering 
\includegraphics[width=0.9\textwidth]{S1a.eps}
\subcaption{Profit - S1a}
\label{jedno}
\end{minipage}
\begin{minipage}{.49\linewidth}
\centering 
\includegraphics[width=0.9\textwidth]{S1b.eps}
\subcaption{Profit - S1b}
\label{dwu}
\end{minipage}
\\
\begin{minipage}{.49\linewidth}
\centering 
\includegraphics[width=0.9\textwidth]{S1c.eps}
\subcaption{Profit- S1c}
\label{cztero}
\end{minipage}
\begin{minipage}{.49\linewidth}
\centering 
\includegraphics[width=0.9\textwidth]{S1d.eps}
\subcaption{Profit - S1d}
\label{mansard}
\end{minipage}
\begin{minipage}{\linewidth}
\centering 
\includegraphics[width=0.6\textwidth]{S1s.eps}
\label{mansard}
\subcaption{Profit - S1s}
\end{minipage}
\caption{EURJPY market results}
\end{figure}
\FloatBarrier

>>>>

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{amsthm}
\usepackage{txfonts}
\usepackage{epstopdf}
\usepackage{placeins}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[table]{xcolor}
\usepackage{array}
\usepackage{subcaption}

@@

\title{Magnitude of simple rules in investment strategies of algorithmic trading}
\headtitle{Magnitude of simple rules in investment strategies of algorithmic trading\dots}
\author{Antoni Wiliński\inst{1}, Piotr Błaszyński\inst{1}, Aneta Bera\inst{1}, \\ Wojciech Nowicki\inst{1}, Katarzyna Buda\inst{1}}
\headauthor{A. One, A. Two}
\affiliation{%
  \inst{1}West Pomeranian University of Technology\\
  Faculty of Computer Science\\
  ul.Żołnierska 49, 71-210 Szczecin Poland\\
  {awilinski,pblaszynski}@wi.ps.pl, @wi.ps.pl
}
\keywords{algorithmic trading, forecasting, financial markets, simple rules, computational intelligence, investment strategies}

@@

\begin{figure}[h]
\centering
\begin{minipage}{.49\linewidth}
\centering 
\includegraphics[width=0.82\textwidth]{S1a.eps}
\subcaption{Profit - S1a}
\label{jedno}
\end{minipage}
\begin{minipage}{.49\linewidth}
\centering 
\includegraphics[width=0.82\textwidth]{S1b.eps}
\subcaption{Profit - S1b}
\label{dwu}
\end{minipage}
\\
\begin{minipage}{.49\linewidth}
\centering 
\includegraphics[width=0.82\textwidth]{S1c.eps}
\subcaption{Profit- S1c}
\label{cztero}
\end{minipage}
\begin{minipage}{.49\linewidth}
\centering 
\includegraphics[width=0.82\textwidth]{S1d.eps}
\subcaption{Profit - S1d}
\label{mansard}
\end{minipage}
\begin{minipage}{\linewidth}
\centering 
\includegraphics[width=0.6\textwidth]{S1s.eps}
\label{mansard}
\subcaption{Profit - S1s}
\end{minipage}
\caption{EURJPY market results}
\end{figure}
\FloatBarrier
